MSB106 - Assignment

### 2023-02-19 MSB106_Assignment.qmd
.

```{r, echo=FALSE}
kable(summary(Commune_Data))
```

```{r, echo=FALSE}
kable(summary(Dentist_Data[3:6]))
```

```{r, echo=FALSE}
kable(summary(Dentist_Data[7:10]))
```

```{r, echo=FALSE}
kable(summary(Dentist_Data[11:12]))
```

```{r, echo=FALSE}
#| label: fig-1
#| tbl-cap: "Capita in retail compared to mall distance"
Commune_Data |>
  ggplot(aes(x = SizeMall, y = Turnover_capita_retail, colour = SizeMall)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "Turnover capita in retail per inhabitant") +
  theme_bw()
```

```{r,echo=FALSE}
#| label: fig-2
#| tbl-cap: "Dentist income compared to CBD distance"
Dentist_Data |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

@@

```{r, echo=FALSE}
Dentist_Data_LIMIT |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) + labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

```{r, echo=FALSE}
Dentist_Data |>
  ggplot(aes(x = DistMal, y = Driftsres, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "EBIT") +
  theme_bw()
```

@@

```{r, echo=FALSE}
huxreg(list("Dentist Revenue" = lm1), statistics = c(N = "nobs", R2 = "r.squared"), const. = "(Intercept)", note = "Note: {stars} T statistics in brackets.")
```

@@

```{r, echo=FALSE}
huxreg(list("Turnover per capita in retail" = lm2), statistics = c(N = "nobs", R2 = "r.squared"), const. = "(Intercept)", note = "Note: {stars} T statistics in brackets.")
```

>>>>

```{r, echo=FALSE}
#|label: tbl-1
#|tbl-cap: "Commune data summary"
kable(summary(Commune_Data))
```

```{r, echo=FALSE}
#|label: tbl-2
#|tbl-cap: "Dentist data summary"
kable(summary(Dentist_Data[3:6]))
```

```{r, echo=FALSE}
#|label: tbl-3
#|tbl-cap: "Dentist data summary"
kable(summary(Dentist_Data[7:10]))
```

```{r, echo=FALSE}
#|label: tbl-4
#|tbl-cap: "Dentist data summary"
kable(summary(Dentist_Data[11:12]))
```

```{r, echo=FALSE}
#| label: fig-1
#| fig-cap: "Capita in retail compared to mall distance"
Commune_Data |>
  ggplot(aes(x = SizeMall, y = Turnover_capita_retail, colour = SizeMall)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "Turnover capita in retail per inhabitant") +
  theme_bw()
```

```{r,echo=FALSE}
#| label: fig-2
#| fig-cap: "Dentist income compared to CBD distance"
Dentist_Data |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

@@

```{r, echo=FALSE}
#| label: fig-3
#| fig-cap: "Dentist income compared to CBD distance"
Dentist_Data_LIMIT |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) + labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

```{r, echo=FALSE}
#| label: fig-4
#| fig-cap: "Dentist EBIT compared to Mall distance"
Dentist_Data |>
  ggplot(aes(x = DistMal, y = Driftsres, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "EBIT") +
  theme_bw()
```

@@

```{r, echo=FALSE}
#|label: tbl-4
#|tbl-cap: "Dentist Revenue MRM"
huxreg(list("Dentist Revenue" = lm1), statistics = c(N = "nobs", R2 = "r.squared"), const. = "(Intercept)", note = "Note: {stars} T statistics in brackets.")
```

@@

```{r, echo=FALSE}
#|label: tbl-5
#|tbl-cap: "Turnover per capita retail MRM"
huxreg(list("Turnover per capita in retail" = lm2), statistics = c(N = "nobs", R2 = "r.squared"), const. = "(Intercept)", note = "Note: {stars} T statistics in brackets.")
```
